Typed Lua

### 2013-06-27 doc/slides/gsoc_proposal/gsoc_proposal.tex
Minor improvements to the presentation about the GSoC proposal

\begin{frame}[fragile]
\frametitle{Gradual Typing Example}
\begin{verbatim}
local function div (x, y)
  if y == 0 then
    return nil,"division by zero"
  end
  return x / y
end

local function div (x:Number, y:Number) -> Any
  if y == 0 then
    return nil,"division by zero"
  end
  return x / y
end
\end{verbatim}
\end{frame}

\subsection{The levels of Gradual Typing}
\begin{frame}
\frametitle{The levels of Gradual Typing}
\begin{itemize}
\item The programmer can gradually migrate to static typing
\item Specially in module boundaries
\begin{enumerate}
\item The programmer write modules that use only dynamic typing.
\item The programmer creates an interface to type a module that
is written using only dynamic typing. This module is not
type checked, but the code that uses this module is.
\item The programmer write modules that use only static typing.
\end{enumerate}
\end{itemize}
\end{frame}

@@

\section{Typed Lua}
\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item A proposal to design a gradual type system for Lua
\begin{itemize}
\item Should be simple enough to preserve existing Lua idioms
\end{itemize}
\item A superset of Lua
\begin{itemize}
\item Type annotations
\item Compile-time type checking
\item Classes
\item Interfaces
\item Modules
\end{itemize}
\end{itemize}
\end{frame}

@@

\subsection{Metatables}
\begin{frame}
\frametitle{Metatables}
\begin{itemize}
\item 294 (15.0\%) of the 1966 files use \textbf{setmetatable}
\item 99 (5.1\%) of the 196 files use \textbf{getmetatable}
\end{itemize}
\end{frame}

\subsection{Table constructor}
\begin{frame}
\frametitle{Table constructor}
\begin{itemize}
\item The table constructor is being used 17369 times in the 1966 files
\begin{itemize}
\item 4391 (25.28\%) times is the empty construct
\item 12975 (74.70\%) times is a constructor with only static keys
\item 3 (0.02\%) times is a constructor with only dynamic keys
\item There is no constructor with static and dynamic keys
\end{itemize}
\end{itemize}
\end{frame}

\subsection{Module}
\begin{frame}
\frametitle{Module}
\begin{itemize}
\item 655 (33.3\%) of the 1966 files use \textbf{return} at the end of the file
\item 602 (30.7\%) of the 1966 files use the function \textbf{module}
\item The rest of the files are plain scripts
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Gradual Typing}
\begin{itemize}
\item The programmer can gradually migrate to static typing
\item Specially in module boundaries
\begin{enumerate}
\item The programmer writes modules that use only dynamic typing.
\item The programmer creates an interface to type a module that
is written using only dynamic typing. This module is not
type checked, but the code that uses this module is.
\item The programmer writes modules that use only static typing.
\end{enumerate}
\end{itemize}
\end{frame}

@@

\section{Typed Lua}
\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item A proposal to design a gradual type system for Lua
\begin{itemize}
\item Should be complex enough to preserve existing Lua idioms
\end{itemize}
\item A superset of Lua
\begin{itemize}
\item Type annotations
\item Compile-time type checking
\item Classes
\item Interfaces
\item Modules
\end{itemize}
\end{itemize}
\end{frame}

@@

\subsection{Metatables}
\begin{frame}
\frametitle{Metatables}
\begin{itemize}
\item 294 (15.0\%) of the 1966 files use \textbf{setmetatable}
\item 99 (5.1\%) of the 1966 files use \textbf{getmetatable}
\end{itemize}
\end{frame}

\subsection{Table constructor}
\begin{frame}
\frametitle{Table constructor}
\begin{itemize}
\item The table constructor is being used 17369 times in the 1966 files
\begin{itemize}
\item 4391 (25.28\%) times it is the empty construct
\item 12975 (74.70\%) times it is a constructor with only static keys
\item 3 (0.02\%) times it is a constructor with only dynamic keys
\item There is no constructor with static and dynamic keys
\end{itemize}
\end{itemize}
\end{frame}

\subsection{Modules}
\begin{frame}
\frametitle{Modules}
\begin{itemize}
\item 616 (31.3\%) of the 1966 files use \textbf{return} at the end of the file
\item 563 (28.7\%) of the 1966 files use the function \textbf{module}
\item 39 (2.0\%) of the 1966 files use \textbf{return} and \textbf{module}
\item The other 748 (38.0\%) files are plain scripts
\item That is, 1218 (62.0\%) of the 1966 files are modules
\end{itemize}
\end{frame}
